Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Cut three small words, keep clarity. Save a line!
Add missing comma.
This comma changes the meaning. "Google Docs and other examples of collaborative
document creation" is what I think you intend, in which case you want the comma.

"Google Docs exemplifies collaborative document creation and also other
technical achievements" is what this means without the comma, and I don't think
that's what you intend.

\begin{enumerate}
\item \emph{Consistent order secure chat}: a chat room system where
    all users see the same message history but the messages never
    traverse a central server and there is no central arbiter
    of truth. The application code itself may still be delivered from
    a central web service. This is the use case that was implemented
    for this paper.
\item \emph{Private multiuser document editing/whiteboard system}:
    Google Docs, among other examples has demonstrated a powerful
    model for collaborative document creation. However, these systems
    all use a centralized servers to coordinate shared state and
    handle browser-to-browser communication. %TODO/CITE
    Using a Raft over WebRTC could enable applications with similar
    functionality but without the central coordination and
    communication.
\item \emph{Browser based network games}: most network games have
    certain states that must be agreed upon by all nodes (e.g. avatar
    dead or alive, etc). This can be achieved with Raft over WebRTC
    without requiring any data to traverse a central server. In
    addition to reducing browser to server bandwidth requirements,
    this may also allow lower latency gaming if game instances are
    partitioned into clusters based on latency.
\end{enumerate}

>>>>

\begin{enumerate}
\item \emph{Consistent order secure chat}: a chat room system where
    all users see the same message history but the messages never
    traverse a central server and there is no central arbiter
    of truth. The application code itself may still be delivered from
    a central web service. This use case was implemented
    for this paper.
\item \emph{Private multiuser document editing/whiteboard system}:
    Google Docs, among other examples, has demonstrated a powerful
    model for collaborative document creation. However, these systems
    all use a centralized servers to coordinate shared state and
    handle browser-to-browser communication. %TODO/CITE
    Using a Raft over WebRTC could enable applications with similar
    functionality but without the central coordination and
    communication.
\item \emph{Browser based network games}: most network games have
    certain states that must be agreed upon by all nodes (e.g. avatar
    dead or alive, etc). This can be achieved with Raft over WebRTC
    without requiring any data to traverse a central server. In
    addition to reducing browser to server bandwidth requirements,
    this may also allow lower latency gaming if game instances are
    partitioned into clusters based on latency.
\end{enumerate}
